# In-Class Programming Activity, Day 12

#Task 1
```{r}
n_cases=100
red_mean=c(1, 0)
green_mean=c(0,-1)
blue_mean=c(-1, 1)
covar_red = cbind(c(3,-1.7),c(-1.7,1))
covar_blue = cbind(c(2,1.5),c(1.5,3))
One=cbind(rnorm(n_cases),rnorm(n_cases))
Two=cbind(rnorm(n_cases),rnorm(n_cases))
Three=cbind(rnorm(n_cases),rnorm(n_cases))
Red=One%*%chol(covar_red)
Green=Two%*%(chol(covar_red))
Blue=Three%*%chol(covar_blue)
Red=Red+matrix(red_mean,nrow=length(Red[,1]),ncol=2,by=TRUE)
Green=Green+matrix(green_mean,nrow=length(Green[,1]),ncol=2,by=TRUE)
Blue=Blue+matrix(blue_mean,nrow=length(Blue[,1]),ncol=2,by=TRUE)
Red=data.frame(x=Red[,1],y=Red[,2],class='Red',stringsAsFactors = FALSE)
Blue=data.frame(x=Blue[,1],y=Blue[,2],class='Blue',stringsAsFactors = FALSE)
Green=data.frame(x=Green[,1],y=Green[,2],class='Green',stringsAsFactors = FALSE)
Same_sigma <- rbind(Red, Green)
Different_sigma <- rbind(Red, Blue)
```

#Task 2
```{r}
library(MASS)
mod_LDA_one <- lda(class ~ x + y, data = Same_sigma)
test_LDA_one <- predict(mod_LDA_one, newdata = Same_sigma)
mod_QDA_one <- qda(class ~ x + y, data = Same_sigma)
test_QDA_one <- predict(mod_QDA_one, newdata = Same_sigma)
```

#Task 3
```{r}
table(Same_sigma$class, test_LDA_one$class)
table(Same_sigma$class, test_QDA_one$class)
```

## Task 4
```{r}
```{r}
n_cases=1000
red_mean=c(1, 0)
green_mean=c(0,-1)
blue_mean=c(-1, 1)
covar_red = cbind(c(3,-1.7),c(-1.7,1))
covar_blue = cbind(c(2,1.5),c(1.5,3))
One=cbind(rnorm(n_cases),rnorm(n_cases))
Two=cbind(rnorm(n_cases),rnorm(n_cases))
Three=cbind(rnorm(n_cases),rnorm(n_cases))
Red=One%*%chol(covar_red)
Green=Two%*%(chol(covar_red))
Blue=Three%*%chol(covar_blue)
Red=Red+matrix(red_mean,nrow=length(Red[,1]),ncol=2)
Green=Green+matrix(green_mean,nrow=length(Green[,1]),ncol=2)
Blue=Blue+matrix(blue_mean,nrow=length(Blue[,1]),ncol=2)
Red=data.frame(x=Red[,1],y=Red[,2],class='Red',stringsAsFactors = FALSE)
Blue=data.frame(x=Blue[,1],y=Blue[,2],class='Blue',stringsAsFactors = FALSE)
Green=data.frame(x=Green[,1],y=Green[,2],class='Green',stringsAsFactors = FALSE)
Same_sigma <- rbind(Red, Green)
Different_sigma <- rbind(Red, Blue)

mod_LDA_two <- lda(class ~ x + y, data = Same_sigma)
test_LDA_two <- predict(mod_LDA_two, newdata = Same_sigma)
mod_QDA_two <- qda(class ~ x + y, data = Same_sigma)
test_QDA_two <- predict(mod_QDA_two, newdata = Same_sigma)
```


## Test statements

```{r}
scoreActivity::score253(12)
```