# Topic 1 Exercises

## 2.4.1

1. Less flexible
2. More flexible

## 2.4.2

## 2.4.3

## 2.4.4

## 2.4.5

## 2.4.6

## 2.4.7

## 2.4.8 (a)
```{r}
college= read.csv("/Users/aarcher/Desktop/Maching Learning/College.csv")
```

## 2.4.8 (b)

```{r}
college=college[,-1]
fix(college)
```

## 2.4.8 (c) (i) 

```{r}
summary(college)
```

## 2.4.8 (c) (ii) 
```{r}
pairs(college[,1:10])
```

## 2.4.8 (c) (iii) 
```{r}
plot(college$Private,college$Outstate)
```

## 2.4.8 (c) (iv) 
```{r}
Elite=rep("No",nrow(college))
Elite[college$Top10perc >50]="Yes"
Elite=as.factor(Elite)
college=data.frame(college ,Elite)
```

```{r}
summary(college)
plot(college$Elite,college$Outstate)
```

## 2.4.8 (c) (v) 
```{r}
par(mfrow=c(2,2))
hist(college$Top25perc,col=2,breaks=20)
hist(college$Top10perc,col=2,breaks=15)
hist(college$Room.Board,col=2,breaks=10)
hist(college$Outstate,col=2,breaks=5)
```

## 2.4.9 (a)  
```{r}
auto_file_name= "/Users/aarcher/Desktop/Maching Learning/Math-253-Assignments/Auto.csv"
Auto<-read.csv(auto_file_name,header=T,na.strings ="?")
Auto=na.omit(Auto)
fix(Auto)
names(Auto)
```

The quantitative variables are mpg, displacement, hoursepower, weight and acceleration. Cylinders, year and origin in the absolute sense is quantitative variable. The qualitative variable is name. Although cylinders, year and origin are represented as numerics, we can treat them as qualitative variables. 

## 2.4.8 (b)

```{r}
range(Auto$mpg)
range(Auto$cylinders)
range(Auto$displacement)
range(Auto$horsepower)
range(Auto$weight)
range(Auto$acceleration)
range(Auto$year)
range(Auto$origin)
```
Mpg: 9.0 - 46.6
Cylinders: 3-8
Displacement: 68 - 455
Horsepower: 46 - 230
Weight: 1613 - 5140
Acceleration: 8.0 - 24.8
Year: 70 - 82
Origin: 1-3

## 2.4.8 (c)
```{r}
mean(Auto$mpg)
mean(Auto$cylinders)
mean(Auto$displacement)
mean(Auto$horsepower)
mean(Auto$weight)
mean(Auto$acceleration)
mean(Auto$year)
mean(Auto$origin)

sd(Auto$mpg)
sd(Auto$cylinders)
sd(Auto$displacement)
sd(Auto$horsepower)
sd(Auto$weight)
sd(Auto$acceleration)
sd(Auto$year)
sd(Auto$origin)
```

Mpg: mean - 23.4, sd - 7.8
Cylinders: mean - 5.47, sd - 1.70
Displacement: mean - 194.4, sd - 104.6
Horsepower: mean - 104.5, sd - 38.5
Weight: mean - 2977.6, sd - 849.4
Acceleration: mean: 15.54, sd - 2.75
Year: mean: 75.98, sd - 3.68
Origin: 1.57, sd - 0.81

## 2.4.8 (d)

```{r}
Auto = Auto[c(-10,-85),]

range(Auto$mpg)
range(Auto$cylinders)
range(Auto$displacement)
range(Auto$horsepower)
range(Auto$weight)
range(Auto$acceleration)
range(Auto$year)
range(Auto$origin)

mean(Auto$mpg)
mean(Auto$cylinders)
mean(Auto$displacement)
mean(Auto$horsepower)
mean(Auto$weight)
mean(Auto$acceleration)
mean(Auto$year)
mean(Auto$origin)

sd(Auto$mpg)
sd(Auto$cylinders)
sd(Auto$displacement)
sd(Auto$horsepower)
sd(Auto$weight)
sd(Auto$acceleration)
sd(Auto$year)
sd(Auto$origin)
```



The range of all the variables remained the same. The mean and standard deviation change for all the variables.



## 2.4.8 (e)

```{r}
Auto$cylinders=as.factor(Auto$cylinders)
Auto$origin= as.factor(Auto$origin)
Auto$year= as.factor(Auto$year)
```

```{r}
par(mfrow=c(2,2))
plot(Auto$cylinders,Auto$mpg)
plot(Auto$year,Auto$mpg)
plot(Auto$origin,Auto$mpg)
```


The mpg as function of cylinder follows parabola. On average, a cylinder of 4 has the highest mpg. 
On average, higher mpg are associated with higher years.
On average,  higher mpg are associated with origin increasing order.

```{r}
par(mfrow=c(3,3))
plot(Auto$horsepower,Auto$mpg)
plot(Auto$weight,Auto$horsepower)
plot(Auto$weight,Auto$mpg)
plot(Auto$displacement,Auto$mpg)
plot(Auto$displacement,Auto$horsepower)

```


Mpg and horsepower are negatively correlated. 
Weight and horsepower are positively correlated.
Weight and mpg are negatively correlated.
Displacement and mpg are negatively correlated.
Displacement and horsepower are positively correlated.

## 2.4.8 (f)

Yes, other variables could be used to predict mpg. Looking at the block and scatter plot of all the variables, you can see there is a strong between mpg and the variables.


